---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/",
  warning = FALSE,
  message = FALSE
)
```

# ggrapid: Create neat & complete ggplot visualizations with as little code as possible

ggrapid enables creation of the most common ggplot-based visualizations fast and with just a few lines of code. ggrapid comes handy when you'd like to do an initial and quick EDA over various columns of your dataset programatically, without the need of writing a lot of custom ggplot code.

## Installation

```{r, eval = FALSE}
# Install development version from GitHub
devtools::install_github("konradsemsch/ggrapid")
```

## Main functions

* plot_density
* plot_boxplot
* plot_deciles
* plot_correlation
* plot_bars
* plot_line

## Simple examples

```{r fig.height=4, fig.width=7}
library(tidyverse)
library(ggrapid)

diamonds %>%
  plot_density(x = carat)
```

```{r}
diamonds %>%
  plot_density(x = carat,
               fill = cut,
               position = "stack")
```

```{r}
diamonds %>%
  plot_density(x = carat,
               fill = cut,
               position = "fill")
```

```{r}
diamonds %>%
  plot_density(x = carat,
               fill = cut,
               facet = cut,
               title = "Write your title here",
               subtitle = "Write your subtitle here",
               caption = "Write your caption here",
               lab_x = "Carat",
               alpha = .5,
               vline = 1)
```

## Complete usage

```{r, eval = FALSE}

```
